---
title: "Which Country has the Highest Covid cases as of 2020 June?"
author: "Maenya"
date: "2025-02-13"
output: html_document
---


# Question: Which Country has the Highest Covid cases as of 2020 June?

# loading the libraries
```{r}
library(tidyverse)
  library(dplyr)
```


  


# loading the data

```{r}
covid <- read.csv("covid.csv")
colnames(covid)
glimpse(covid)

```



# checking for missing data
```{r}
colSums(is.na(covid))

missing_percentage <- colSums(is.na(covid)) / nrow(covid) * 100
print(missing_percentage)
```




# Selecting the columns we will focus on
```{r}
covid_select <- covid %>%
  select("Country_Region", "positive", "total_tested")
view(covid_select)
```





# Putting all the information from all teh different countries together
```{r}
covid_sum <- covid_select  %>% 
  group_by(Country_Region) %>% 
  summarise(tested = sum(total_tested, na.rm = TRUE), 
            positive = sum(positive, na.rm = TRUE)) %>%
            arrange(desc(positive)) 

view(covid_sum)
```




# Which countries have high covid cases against teh tested ?
```{r}
covid_sum %>%
  arrange(desc(positive),10)
```


The covid positive cases as per country are as below:
```{r}
covid_sum %>%
  arrange(desc(positive))
```


The top 10 countries with highest Covid cases are;

```{r}
covid_sum %>%
  select ("Country_Region", "positive") %>%
  arrange(desc(positive),10)
```


# Creating a visual for the same
```{r}

ggplot(covid_sum %>% head(10), aes(x = reorder(Country_Region, positive), y = positive)) +
  geom_col(fill = "blue") +  # Use a blue color for the bars
  coord_flip() +  # Flip the axes for better readability
  labs(title = "Top 10 Countries with Highest COVID-19 Cases",
       x = "Country",
       y = "Number of Positive Cases") +
  theme_minimal()
```


### Conclusion

 Based on the provided data, USA, Italy, Canada, Turkey and Bangladesh had the highest positive Covid cases globally. 
